Automated topic naming to support analysis of software maintenance activities

### 2010-08-18 icse/icse2011.tex
participants -> stakeholders

Topics in software engineering practice refer to specific `threads' between project participants. These topics can include particular requirements, maintenance requests, bug fixes or other software engineering tasks. %NEIL: define topic specifically as akin to email 'thread'. It sounded too vague. Also changed from 'developers' to 'participants' because developers sounds too coding oriented. Our work could apply to testers, users, etc.
In addressing a topic of development participants often produce or modify multiple development artifacts.
%
These artifacts can include source code, bug reports, revisions to source code, and test cases. 
%
Topics can be in several potential states: they may not be immediately resolved, they may re-occur, yet others are only dealt with briefly  (e.g., a bug report that is closed).
% semi-automatically sounds too uncertain. I think the introduction can be more muscular and bold. Don't give the reviewer any room to start doubting.
The goal of concept location and topic analysis research is to recover these topics and the related software artifacts.
% get neil's data mining point in there
To date, the results of topic analysis and concept location are project specific, and not globally generalizable.
% get the interpretation aspect
Much of the current research stops short of interpreting the purpose of the topic. That is, extracted topics are usually manually named and labelled by those who read the topic words.
% 
In this paper we propose a method of interpreting and labelling topics, and their related artifacts, that is generalizable and relevant to multiple projects.

@@

\begin{figure*}
  \centering
  % hi-res version
  %\includegraphics[height=.55\textheight]{maxdb-time-smear-plot-Equal}
  \includegraphics[width=\textwidth]{figures/maxdb-timeline}
  % \includegraphics[height=.57\textheight]{small-maxdb-time-smear-plot-Equal}
 % \caption{MaxDB 7.500: Labelled topics related to non-functional software qualities plotted over time, continuous topics are trends that occur across time}
  \caption{MaxDB 7.500: NFRs over time. Topic frequency relative to that quality is mapped to alpha (transparency) value.}
 \label{fig:maxdb}
\end{figure*}

\begin{figure*}%[h]
  \centering
 %\includegraphics[width=.97\textwidth]{mysql-time-smear-plot-Equal}
  %\includegraphics[width=.97\textwidth]{small-mysql-time-smear-plot-Equal}
  \includegraphics[width=\textwidth]{figures/mysql-timeline}
  \caption{MySQL 3.23: NFRs over time. Topic frequency relative to that quality is mapped to alpha (transparency) value.}
  \label{fig:mysql}
\end{figure*}

@@

We demonstrated that static but domain-specific knowledge can improve unsupervised labelling of extracted topics. Our \textsf{exp2} experiment used small accurate word bags to label topics but performed just as well as \textsf{exp3}, which used many more general terms from WordNet. We then showed that with some supervision, and by using efficient machine learners based on Naive Bayesian classifiers, we could improve the accuracy of automatic labelling topics even further.

>>>>

Topics in software engineering practice refer to specific `threads' between project stakeholders. These topics can include particular requirements, maintenance requests, bug fixes or other software engineering tasks. %NEIL: define topic specifically as akin to email 'thread'. It sounded too vague. Also changed from 'developers' to 'stakeholders' because developers sounds too coding oriented. Our work could apply to testers, users, etc.
In addressing a topic of development stakeholders often produce or modify multiple development artifacts.
%
These artifacts can include source code, bug reports, revisions to source code, and test cases. 
%
Topics can be in several potential states: they may not be immediately resolved, they may re-occur, yet others are only dealt with briefly  (e.g., a bug report that is closed).
% semi-automatically sounds too uncertain. I think the introduction can be more muscular and bold. Don't give the reviewer any room to start doubting.
The goal of concept location and topic analysis research is to recover these topics and the related software artifacts.
% get neil's data mining point in there
To date, the results of topic analysis and concept location are project specific, and not globally generalizable.
% get the interpretation aspect
Much of the current research stops short of interpreting the purpose of the topic. That is, extracted topics are usually manually named and labelled by those who read the topic words.
% 
In this paper we propose a method of interpreting and labelling topics, and their related artifacts, that is generalizable and relevant to multiple projects.

@@

\begin{figure*}[ht]
\centering
\subfigure[MaxDB 7.500]{
\includegraphics[width=\textwidth]{figures/maxdb-timeline-all}
\label{fig:mysql-timeline}
}
\subfigure[MySQL 3.23]{
\includegraphics[width=\textwidth]{figures/mysql-timeline-all}
\label{fig:maxdb-timeline}
}
\label{fig:timelines}
\caption[]{NFRs over time. Numbers represent topics labelled with that quality. Box intensity (saturation) is mapped to label frequency relative to the largest label value.
\todo[inline]{better discussion}
}
\end{figure*}

% 
% \begin{figure*}
%   \centering
%   % hi-res version
%   %\includegraphics[height=.55\textheight]{maxdb-time-smear-plot-Equal}
%   \includegraphics[width=\textwidth]{figures/maxdb-timeline-all}
%   % \includegraphics[height=.57\textheight]{small-maxdb-time-smear-plot-Equal}
%  % \caption{MaxDB 7.500: Labelled topics related to non-functional software qualities plotted over time, continuous topics are trends that occur across time}
%   \caption{MaxDB 7.500: NFRs over time. Numbers represent topics labelled with that quality. Box intensity (saturation) is mapped to label frequency relative to the largest label value.}
%  \label{fig:maxdb}
% \end{figure*}
% 
% \begin{figure*}%[h]
%   \centering
%  %\includegraphics[width=.97\textwidth]{mysql-time-smear-plot-Equal}
%   %\includegraphics[width=.97\textwidth]{small-mysql-time-smear-plot-Equal}
%   \includegraphics[width=\textwidth]{figures/mysql-timeline-all}
%   \caption{MySQL 3.23: NFRs over time. Topic frequency relative to that quality is mapped to alpha (transparency) value.}
%   \label{fig:mysql}
% \end{figure*}

@@

% What did we do
% What did we show
% What did we do that was new?

% use domain knowledge
We demonstrated that static but domain-specific knowledge can improve unsupervised labelling of extracted topics. 
Our \textsf{exp2} experiment used small accurate word bags to label topics but performed just as well as \textsf{exp3}, which used many more general terms from WordNet.
We then showed that with some supervision, and by using efficient machine learners based on Naive Bayesian classifiers, we could improve the accuracy of automatic labelling topics even further.
